---
title: "Ulrik Lyngs <br> Curriculum vitae"
output:
  pagedown::html_paged:
    css: ["css/bootstrap-5.2.1.min.css", "css/two-col-cv.css"]
    number_sections: false
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(glue)
library(fontawesome)
library(readxl)
library(lubridate)
source("R/utility-functions.R")

cv_entries <- read_excel("cv_data.xlsx", sheet = "cv_entries") |> 
  mutate(year = year(date))
publications <- read_excel("cv_data.xlsx", sheet = "publications") |> 
  mutate(year = year(date))
```


::: {.row}

:::::: {.col-8 .summary}

# Research summary
**Aims**---to develop and evaluate design patterns that help people self-regulate their use of smartphones and laptops.\
**Methods**---controlled studies, user surveys, interviews, co-design workshops, web scraping, behaviour logging.

**I am passionate about** open and transparent research. Since 2018, I have shared materials, analysis scripts, and data for all my first-authored work, and written my papers as reproducible documents in [R Markdown](https://rmarkdown.rstudio.com).

::::::

:::::: {.col-4}

# Contact {.box}

::::::::: {.info-box}

| Center | Left |
|:------:|:-----|
| `r fa("map-marker-alt")`| Dept. of Computer Science, University of Oxford |
| `r fa("envelope")` | ulrik.lyngs@cs.ox.ac.uk |
| `r fa("globe")` | [ulriklyngs.com](https://ulriklyngs.com) |
| `r fa("github")` | [ulyngs](https://github.com/ulyngs) |
 
:::::::::

::::::

:::

::: {.row}

:::::: {.col-6 .left}

# Awards and honours
 
```{r}
cv_entries |> 
  filter(type == 'awards', short_cv == "y") |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |>  
  select(year, what) |> 
  kable()
```

# Selected major grants
 
```{r}
cv_entries |>
  filter(type == 'major_grants', short_cv == "y") |>
  mutate(what = if_else(is.na(additional_info),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}"),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}"))) |>
  select(year, what) |>
  kable()
```

::::::

:::::: {.col-6 .right}

# Education

```{r}
cv_entries |> 
  filter(type == 'education') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |> 
  select(year, what) |> 
  kable()
```

# Selected teaching experience
```{r}
cv_entries |> 
  filter(type == 'teaching', short_cv == "y") |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>",
         "{additional_info}")) |> 
  select(year, what) |> 
  kable()
```

::::::

:::

<!-- you might want to manually insert page breaks -->
<br class="pageBreak" />

::: {.row .pagetwo}

:::::: {.col-6 .left}

# Selected talks {.talks}
```{r}
cv_entries  |>  
  filter(type == 'talk', short_cv == "y") |> 
  # add commas as appropriate
  mutate(where = if_else(!is.na(where) & !is.na(institution), glue(", {where}"), where),
         department = if_else(!is.na(department), glue(", {department}"), department),
         additional_info = if_else(!is.na(additional_info), glue(", {additional_info}"), "")) |> 
  # add slide and video links
  mutate(slides = if_else(!is.na(slides), glue("<a href={slides}>Slides</a>"), ""),
         video = if_else(!is.na(video), glue("<a href={video}>Video</a>"), "")) |> 
  # put it all together
  mutate(what = glue("<span class='cv-entry-title'>{institution}{where}</span>{department}{additional_info}<br>",
                      "<span style='display:inline-block;' class='talk-title'>{what}</span>", 
                     .na = "")) |> 
  select(year, what) |> 
  kable()
```

::::::

:::::: {.col-6 .right}

# Selected media & panels
```{r}
cv_entries |> 
  filter(type == 'media' | type == 'talk-podcast' | type == 'talk-panel') |>
  filter(short_cv == "y") |> 
  # format the translation
  mutate(what_translation = if_else(!is.na(what_translation), glue("({what_translation})"), what_translation)) |> 
  replace_na(list(what_translation = "")) |> 
  # put it all together
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what} *{what_translation}*")) |>
  select(year, what) |> 
  kable()
```

# Professional development {.prof-dev}
```{r}
cv_entries |> 
  filter(type == 'prof-dev') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |> 
  select(year, what) |> 
  kable()
```

# Selected service
```{r}
cv_entries |> 
  filter(type == 'service', short_cv == "y") |> 
  mutate(where = if_else(!is.na(url), glue("[{where}]({url})"), where)) |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span> {where}")) |>
  arrange(desc(date_end), desc(date)) |> 
  select(year, what) |> 
  kable()
```

::::::
:::
