---
output:
  pagedown::html_paged:
    number_sections: false
    css: ["css/academic_cv.css"]
links-to-footnotes: true
knit: pagedown::chrome_print
---

<style>
:root{
  --last-updated: "\00a0 \00a0 \00a0 \00a0 Last updated: `r format(Sys.Date(), '%B, %Y')`";
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(glue)
library(fontawesome)
library(readxl)
library(lubridate)
source("R/utility-functions.R")

cv_entries <- read_excel("cv_data.xlsx", sheet = "cv_entries")  |> 
  # provide range for entries with a year_end (e.g. '2013-2016')
  mutate(year_end = if_else(date_end == "present", "present", str_sub(date_end, start = 1, end = 4)),
         year = if_else(!is.na(year_end) & year(date) != year_end,
                        str_c(year(date), " --- ", year_end),
                        as.character(year(date))))

publications <- read_excel("cv_data.xlsx", sheet = "publications")  |> 
  mutate(year = year(date),
         venue_abbrev = if_else(is.na(venue_abbrev), "", str_c(venue_abbrev, ": ")))

```

::: {.title-and-contact}

:::::: {.title}
<h1 class="title">Ulrik Lyngs</h1>
::::::

:::::: {.contact-info}
ulrik.lyngs@cs.ox.ac.uk  \
https://ulriklyngs.com
::::::

:::

## Research summary
::: {.research-interests}

:::::: {.spacer}
::::::

:::::: {.interests}
**Aims---**to develop and evaluate design patterns that help people self-regulate their use of smartphones and laptops.
<br>
**Methods---**controlled studies, user surveys, interviews, co-design workshops, web scraping, behaviour logging.

**I am passionate about** open and transparent research. 
Since 2018, I have shared materials, analysis scripts, and data for all my first-authored work, and written my papers as reproducible documents in [R Markdown](https://rmarkdown.rstudio.com).
::::::
:::

::: {.cv-entries}
## Research positions
```{r}
cv_entries |>  
  filter(type == 'research_positions', is.na(exclude)) |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span><br>",
                     "{where}"
                     )) |>  
  select(year, what) |> 
  kable()
```



## Education
```{r}
cv_entries |> 
  filter(type == 'education') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>", 
                      "{additional_info}<br>",
                      "<span class='thesis-title'>{additional_info2}</span>")) |> 
  select(year, what) |> 
  kable()
```

## Major grants and funding
```{r}
cv_entries |>
  filter(type == 'major_grants') |>
  mutate(what = if_else(is.na(additional_info),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}"),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}.<br>{additional_info}"))) |>
  select(year, what) |>
  manual_page_break_after_row("what", "Impact Acceleration") |> 
  kable()
```

## Awards & honours
```{r}
cv_entries |> 
  filter(type == 'awards') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |>  
  blank_year_when_repeated() |> 
  select(year, what) |> 
  kable()
```


## Publications {.three-split}

:::::: {.grid-container-publications}
::::::::: {.conference-publication-heading}
<h3>Conference publications <br><span class="review-note">(fully reviewed, archival)</span></h3>
:::::::::

::::::::: {.conference-note}
<h3>In computer science, top-tier conferences (<30% acceptance rate) are as, or more impactful than journals, see doi.org/fgjt2h</h3>
:::::::::
::::::

<br class="pageBreak">

```{r}
publications_formatted <- publications |> 
  mutate(authors = map_chr(authors, replace_first_names_in_author_list_with_initial_and_dot), # e.g. U. Lyngs instead of Ulrik Lyngs
         authors = str_replace(authors, "U\\. Lyngs", "*U\\. Lyngs*"))    # make my name italic

publications_formatted |>
  filter(type == "conference paper") |> 
  # insert appropriate icon for paper awards (and start with a line break)
  mutate(award = case_when(
    !is.na(award) & str_detect(award, "honourable") ~ glue("<br>", fa("award"), " <span class='publication-award'>{award}</span>"),
    !is.na(award) ~ glue("<br>", fa("trophy"), " <span class='publication-award'>{award}</span>"),
    TRUE ~ ""
  )) |>
  # create citations
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors}</span><br>",
                         "<span class='publication-venue'>{venue_abbrev}{venue}</span>{award}")) |> 
  # number entries with a prefix
  add_leading_zeroes_and_letter("C") |> 
  blank_year_when_repeated() |> 
  select(year, number, citation) |>
  manual_page_break_after_row("citation", "Third party tracking") |> 
  knitr::kable()
```


<h3>Journal articles <span class="review-note">(fully reviewed, archival)</span></h3>

```{r}
publications_formatted |>
  filter(type == "journal article") |> 
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors}</span><br>",
                         "<span class='publication-venue'>{venue_abbrev}{venue}</span>")) |> 
  add_leading_zeroes_and_letter("J") |> 
  blank_year_when_repeated() |>
  select(year, number, citation) |>
  knitr::kable()
```



### Book chapters

```{r}
publications_formatted |> 
  filter(type == "book chapter") |> 
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors}</span><br>",
                         "<span class='publication-venue'>{venue_abbrev}{venue}</span>")) |>
  add_leading_zeroes_and_letter("B") |> 
  blank_year_when_repeated() |>
  select(year, number, citation) |>
  knitr::kable()

```

<h3>Extended abstracts and workshop papers <br><span class="review-note">(lightly reviewed)</span></h3>

```{r}
publications_formatted |>
  filter(type == "extended abstract" | type == "workshop paper") |> 
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors}</span><br>",
                         "<span class='publication-venue'>{venue_abbrev}{venue}</span>")) |>
  add_leading_zeroes_and_letter("A") |> 
  blank_year_when_repeated() |>
  select(year, number, citation) |>
  manual_page_break_after_row("citation", "Designing to Support Autonomy") |> 
  knitr::kable()
```

## Publicly available research code & data
```{r}
pubs_w_number <- publications |> 
  select(type, authors, date, year, title, materials) |> 
  mutate(inclusive_type = if_else(type == "workshop paper" | type == "extended abstract", "abstract", type)) |> 
  group_by(inclusive_type) |> 
  arrange(date) |> 
  mutate(number = row_number(),
         number = case_when(
           inclusive_type == "conference paper" ~ glue("[C{number}]"),
           inclusive_type == "journal article" ~ glue("[J{number}]"),
           inclusive_type == "abstract" ~ glue("[A{number}]"),
           TRUE ~ ""
         ))

public_code <- cv_entries |> 
  filter(type == 'open_research' & is.na(exclude)) |> 
  select(what, additional_info) |> 
  rename(title = additional_info) |> 
  left_join(pubs_w_number)

public_code |> 
  mutate(what = glue("<span class='cv-entry-title'>{what} {number}</span><br>", 
                      "{authors}<br>",
                      "{materials}")) |> 
  arrange(desc(date)) |> 
  select(year, what) |> 
  blank_year_when_repeated() |> 
  manual_page_break_after_row("what", "Before and after GDPR") |>
  kable()
```

## Research dissemination
### Press
```{r}
cv_entries |> 
  filter(type == 'media') |>
  mutate(what = if_else(is.na(what_translation),
    glue("<span class='cv-entry-title'>{where}</span>, {what}"),
    glue("<span class='cv-entry-title'>{where}</span>, {what} (*{what_translation}*)"))) |>
  #manual_page_break_after_row("what", "Kortsluttet") |> 
  select(year, what) |> 
  kable()
```



### Podcasts {.three-split}
```{r}
cv_entries |> 
  filter(type == 'talk-podcast') |> 
  mutate(what_translation = ifelse(!is.na(what_translation), str_c("(", what_translation, ")"), what_translation)) |> 
  replace_na(list(what_translation = "")) |> 
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what} <span class='cv-entry-translation'>{what_translation}</span>")) |>
  add_leading_zeroes_and_letter("Pod") |> 
  blank_year_when_repeated() |> 
  select(year, number, what) |> 
  knitr::kable()

```


<br class="pageBreak">

### Talks {.three-split}

:::::: {.conference-presentations-omitted}
All first-authored conference publications listed above were also presented as talks at their respective conferences and are not listed again in this section.
::::::

```{r}
cv_entries |> 
  filter(type == 'talk', is.na(exclude)) |> 
  # add commas as appropriate
  mutate(where = if_else(!is.na(where) & !is.na(institution), glue(", {where}"), where),
         department = if_else(!is.na(department), glue(", {department}"), department),
         slides = if_else(!is.na(slides), glue("<a href={slides}>Slides</a>"), ""),
         video = if_else(!is.na(video), glue("<a href={video}>Video</a>"), "")) |>
  mutate(additional_info = if_else(!is.na(additional_info), glue(", {additional_info}"), "")) |> 
  mutate(what_translation = ifelse(!is.na(what_translation), str_c("(", what_translation, ")"), what_translation)) |> 
  replace_na(list(what_translation = "")) |> 
  mutate(what = glue("<span class='cv-entry-title'>{institution}{where}</span>{department}{additional_info}<br>",
                      "<span style='display:inline-block;' class='talk-title'>{what}</span> <span class='cv-entry-translation'>{what_translation}</span>", 
                     .na = "")) |> 
  add_leading_zeroes_and_letter("T") |> 
  blank_year_when_repeated() |> 
  select(year, number, what) |> 
  manual_page_break_after_row("what", "dvanced Visual Interfaces") |> 
  manual_page_break_after_row("what", "nline lecture series") |> 
  manual_page_break_after_row("what", "Distraction and Self-Regulation in Social Machines") |>
  knitr::kable()

```

### Discussion panels {.three-split}
```{r}
cv_entries |> 
  filter(type == 'talk-panel') |>
  mutate(additional_info = if_else(is.na(additional_info), "", additional_info)) |> 
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what},  {additional_info}")) |>
  add_leading_zeroes_and_letter("D") |> 
  blank_year_when_repeated() |> 
  select(year, number, what) |> 
  knitr::kable()

```



### Poster presentations {.three-split}
```{r}
cv_entries |> 
  filter(type == 'poster') |>
  mutate(where = if_else(!is.na(where) & !is.na(institution), glue(", {where}"), where),
         department = if_else(!is.na(department), glue(", {department}"), department)) |>
  mutate(additional_info = if_else(!is.na(additional_info), glue(", {additional_info}"), "")) |> 
  mutate(what = glue("<span class='cv-entry-title'>{institution}{where}</span>{department}{additional_info}<br>",
                      "<span style='display:inline-block;' class='talk-title'>{what}</span>", 
                     .na = "")) |> 
  add_leading_zeroes_and_letter("P") |> 
  blank_year_when_repeated() |> 
  select(year, number, what) |>
  manual_page_break_after_row("what", "2018 CHI Conference") |> 
  knitr::kable()

```


### Blog posts {.three-split}
```{r}
cv_entries |> 
  filter(type == 'pop-writing') |>
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what}")) |>
  add_leading_zeroes_and_letter("B") |> 
  blank_year_when_repeated() |> 
  select(year, number, what) |> 
  knitr::kable()
```


<!-- <br class="pageBreak"> -->

## Teaching experience
```{r}
cv_entries |> 
  filter(type == 'teaching') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>",
         "{additional_info}")) |> 
  select(year, what) |> 
  manual_page_break_after_row("what", "Instructor, Digital Humanities") |>
  kable()
```

<!-- <br class="pageBreak"> -->

## Software
### R packages
```{r}
cv_entries |> 
  filter(type == 'software-rstats' & is.na(exclude)) |> 
  replace_na(list(where = "", additional_info = "")) |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |>
  arrange(desc(year)) |> 
  mutate(row_number = row_number()) |> 
  select(year, what) |> 
  kable()
```

<!-- <br class="pageBreak"> -->

### Apps
```{r}
cv_entries |> 
  filter(type == 'software-browser-extensions' & is.na(exclude)) |> 
  replace_na(list(where = "", additional_info = "")) |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |>
  arrange(desc(date_end), desc(date)) |> 
  mutate(row_number = row_number()) |> 
  select(year, what) |> 
  kable()

```


## Service
```{r}
cv_entries |> 
  filter(type == 'service') |> 
  mutate(where = if_else(!is.na(url), glue("[{where}]({url})"), where)) |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span> {where}")) |>
  arrange(desc(date_end), desc(date)) |> 
  select(year, what) |> 
  # manual_page_break_after_row("what", "DPhil representative in the Computer Science Graduate Society") |> 
  kable()
```


<!-- <br class="pageBreak"> -->

## Selected work experience
```{r}
cv_entries |> 
  filter(type == 'work', is.na(one_column_paged)) |> 
  mutate(additional_info = replace_na(additional_info, "")) |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>",
                     "{additional_info}")) |> 
  select(year, what) |>
  #manual_page_break_after_row("what", "RoboTIPS") |> 
  kable()
```

<br class="pageBreak">

## Professional development
```{r}
cv_entries |> 
  filter(type == 'prof-dev') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |>
  select(year, what) |> 
  kable()
```

## Minor grants and funding
```{r}
cv_entries |>
  filter(type == 'minor_grants') |>
  mutate(what = if_else(!is.na(additional_info),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}.<br> ", 
                             "{additional_info}"),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}"))) |>
  blank_year_when_repeated() |> 
  select(year, what) |>
  # manual_page_break_after_row("what", "US research travel") |>
  kable()
```

<!-- <br class="pageBreak"> -->

## Personal skills & volunteering {.packages}
```{r}
cv_entries |>
  filter(type == 'volunteering') |>
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |>
  mutate(what = if_else(!is.na(additional_info), glue("{what}<br>{additional_info}"), what)) |>
  arrange(desc(date), desc(date_end)) |> 
  select(year, what) |>
  manual_page_break_after_row("what", "Head of Entertainment") |>
  kable()
```

:::

<!-- <br class="pageBreak"> -->

# Links
