---
output:
  html_document:
    css: css/website-cv.css
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(glue)
library(fontawesome)
library(DT)
library(lubridate)
library(readxl)
source("R/utility-functions.R")

cv_entries <- read_excel("cv_data.xlsx", sheet = "cv_entries") |> 
  mutate(year = year(date))
publications <- read_excel("cv_data.xlsx", sheet = "publications") |> 
  mutate(year = year(date))
```

# Summary

I am passionate about using insights from the behavioural neurosciences to **design digital technology that is sensitive to human limitations and biases**, particularly in relation to attention and self-regulation.

My **academic and professional background** is highly interdisciplinary, and I try to integrate best practices from many work spheres, such as using tools from large-scale event management to structure academic projects.

My **personal interests** include backpacking, samatha meditation, dancing (Cuban salsa and swing), surfing, and playing music (often with my concept band the [Karaoke Collective](https://karaokecollective.com)).

[`r fa("download")` CV as PDF](https://ulriklyngs.com/pdfs/academic_cv.pdf)

# Academia {.domain-header}
##  Research positions
```{r}
cv_entries |>  
  filter(type == 'research_positions', is.na(exclude)) |>
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span><br>", 
                      where)) |> 
  select(year, what) |> 
  kable(escape = FALSE)
```

## Education
```{r}
cv_entries |> 
  filter(type == 'education') |> 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span>, ", where,
                      "<br>", additional_info,
                      "<br>", additional_info2)) |> 
  select(year, what) |> 
  kable(escape = FALSE)

```

## Awards and honours
```{r}
cv_entries |> 
  filter(type == 'awards') |>
  filter(!(website == "n") | is.na(website)) |> 
  mutate(what = if_else(
    !is.na(where),
    str_c("<span class='cv-entry-title'>", what, "</span>, ", where),
    str_c("<span class='cv-entry-title'>", what, "</span>"))
  ) |> 
  blank_year_when_repeated() |> 
  select(year, what) |> 
  kable(align = c("l", "l"), escape = FALSE)
```
 
## Grants and funding
```{r}
cv_entries |> 
  filter(type == 'minor_grants' | type == 'major_grants',
         is.na(exclude)) |>
  filter(!(website == "n") | is.na(website)) |> 
  mutate(what = if_else(
    !is.na(additional_info),
    str_c("<span class='cv-entry-title'>", what, "</span>, ", where, "<br>", additional_info),
    str_c("<span class='cv-entry-title'>", what, "</span>, ", where))
  ) |> 
  arrange(date_end) |> 
  blank_year_when_repeated() |> 
  select(year, what) |> 
  kable(align = c("l", "l"), escape = FALSE) 
```


## Research dissemination {.tabset .output-header}
### Talks
```{r}
cv_entries |> 
  filter(type == 'talk') |> 
  mutate(where = str_replace(where, "\\[([^]]*)\\]\\(([^\\s^\\)]*)[\\s\\)]", "<a href='\\2'>\\1</a>")) |> 
  mutate(what = glue::glue("<em>{what}</em>, {where}", .na = "")) |> 
  select(date, what) |> 
  arrange(desc(date)) |> 
  mutate(date = str_c(year(date),
                      ", ",
                      month(date, label = TRUE))) |> 
  datatable(rownames = FALSE, escape = FALSE, class = 'row-border', options = list(
  pageLength = 10
))

```

### Posters {.posters}
```{r}
cv_entries |> 
  filter(type == 'poster') |>
  mutate(what = str_c("*", what, "*, ", where)) |> 
  select(year, what) |> 
  arrange(desc(year)) |> 
  kable()
```

### Media {.media}
```{r}
cv_entries |> 
  filter(type == 'media') |>
  select(year, what) |> 
  kable()
```



## Teaching experience

```{r}
cv_entries |> 
  filter(type == 'teaching') |> 
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='cv-entry-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info),
    str_c("<span class='cv-entry-title'>", what, "</span><br class='work-break'>", where))) |> 
  select(year, what) |> 
  kable(escape = FALSE)
  
```

## Service
```{r}
cv_entries |> 
  filter(type == 'service') |> 
  mutate(where = ifelse(!is.na(url), str_c("[", where, "](", url, ")"), where)) |> 
  mutate(what = ifelse(!is.na(additional_info),
                       str_c("<span class='cv-entry-title'>", what,
                      "</span><br class='work-break'>", 
                      where),
                      str_c("<span class='cv-entry-title'>", what,
                      "</span><br class='work-break'>", 
                      where))) |> 
  arrange(desc(date_end), desc(date)) |> 
  select(year, what) |> 
  kable(escape = FALSE)

```


# Work
## Selected employments
```{r}
cv_entries |> 
  filter(type == 'work', is.na(website)) |> 
  mutate(additional_info = replace_na(additional_info, "")) |> 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info)) |> 
  arrange(desc(date)) |> 
  select(year, what) |> 
  kable(escape = FALSE)
```

## Professional development
```{r}
cv_entries |> 
  filter(type == 'prof-dev') |> 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span>, ", where)) |> 
  select(year, what) |> 
  kable(align = c("l", "l"), escape = FALSE)
```

# Technical
## Skills
```{r}
cv_entries |> 
  filter(type == 'technical') |> 
  mutate(icon = case_when(
    str_detect(what, "data analysis") ~ "chart-bar",
    str_detect(what, "research") ~ "flask",
    str_detect(what, "Web") ~ "laptop"
  )) |> 
  rowwise() |> 
  mutate(what = str_c(fa(icon), "&nbsp;<span class='cv-entry-title'>", what, "</span> ", additional_info)) |> 
  select(type, what) |> 
  mutate(type = "") |> 
  kable(escape=FALSE)
```

## R packages
```{r}
cv_entries |> 
  filter(type == 'software-rstats' & is.na(exclude)) |> 
  replace_na(list(where = "", additional_info = "")) |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |>
  arrange(desc(year)) |> 
  mutate(row_number = row_number()) |> 
  select(year, what) |> 
  kable(escape=FALSE)
```

## Apps
```{r}
cv_entries |> 
  filter(type == 'software-browser-extensions' & is.na(exclude)) |> 
  replace_na(list(where = "", additional_info = "")) |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |>
  arrange(desc(year)) |> 
  mutate(row_number = row_number()) |> 
  select(year, what) |> 
  kable(escape=FALSE)
```


# Personal
## Skills & volunteering
```{r}
cv_entries |>
  filter(type == 'volunteering') |>
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span><br class='work-break'>", where)) |>
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) |>
  arrange(desc(date_end)) |> 
  select(year, what) |>
  kable(escape = FALSE) 
```
