---
title: "Ulrik Lyngs: CV"
output:
  html_document:
    css: [make-cv-like-other.css, one-column-cv.css, "website-page.css", "style.css", "academicons-1.8-2.6/css/academicons.min.css"]
    toc: true
    toc_float: true

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)

#### publications #####
publications <- readxl::read_xlsx("cv_data/publications.xlsx")

#### all other entries #####
cv_entries <- readxl::read_xlsx("cv_data/cv_entries.xlsx")

```

<br>

# Summary

I am passionate about using insights from the behavioural neurosciences to **design digital technology that is sensitive to human limitations and biases**, particularly in relation to attention and self-regulation.

My **academic and professional background** is highly interdisciplinary, and I try to integrate best practices from many work spheres, such as using tools from large-scale event management to structure academic projects.

My **personal interests** include travelling & couchsurfing, samatha meditation, dancing (Cuban salsa and swing), and playing music (whatever instruments I can get my hands on, and ideally with the [Karaoke Collective](https://karaokecollective.com))

Download a brief version of [my CV as PDF](https://github.com/ulyngs/pagedown-cv/raw/master/_pdfs/lyngs_cv_2019_april.pdf).

<br>

# Academic
## Education {.education .nohead}
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  mutate(year = str_c(year_begin, " --- ", year_end)) %>% 
  select(year, what) %>% 
  kable()
```

## Grants and Awards {.grants .nohead}
```{r}
cv_entries %>% 
  filter(type == 'grants_and_awards') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year_begin, what) %>% 
  kable()
```

## Talks and poster presentations {.tabset .output-header}
<!-- ### Publications {.nohead .publications} -->
<!-- ```{r} -->
<!-- publications_table <- publications %>% -->
<!--   arrange(desc(year), type) %>% -->
<!--   mutate(author_year = str_c(authors, " (", year, "). ")) %>% -->
<!--   #mutate(author_year = str_c("*", authors, " (", year, ")*. ")) %>%  #italicise authors and year -->
<!--   mutate(title = ifelse(!is.na(url), str_c("[", title, "](", url, ")"), title)) %>% #turn title into link -->
<!--   #mutate(title = str_c("<span style='text-decoration: underline'>", title, "</span>")) %>% #underline title -->
<!--   mutate(citation = ifelse(!is.na(award),  -->
<!--                            str_c(author_year, title, venue, "<i class='fas fa-award'></i><em>", award, "</em>", sep = " "), -->
<!--                            str_c(author_year, title, venue, sep = " "))) %>% -->
<!--   mutate(citation = str_replace(citation, "Lyngs, U.", "__Lyngs, U.__")) # make my name bold -->

<!-- publications_table %>% -->
<!--   filter(type != "master's thesis") %>%  -->
<!--   select(type, citation) %>% -->
<!--   knitr::kable() -->

<!-- ``` -->

### Talks {.nohead .talks}
```{r}
cv_entries %>% 
  filter(type == 'talk') %>% 
  mutate(what = str_c("*", what, "*, ", where)) %>% 
  select(year_begin, what) %>% 
  kable()
```

### Posters {.nohead .posters}
```{r}
cv_entries %>% 
  filter(type == 'poster') %>%
  mutate(what = str_c("*", what, "*, ", where)) %>% 
  select(year_begin, what) %>% 
  arrange(desc(year_begin)) %>% 
  kable()
```

## Media coverage {.media .nohead}
```{r}
cv_entries %>% 
  filter(type == 'media') %>%
  select(year_begin, what) %>% 
  kable()
```

## Service {.service .nohead}
```{r}
cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(year_end = ifelse(year_end == "present", "", year_end)) %>% 
  mutate(where = ifelse(!is.na(url), str_c("[", where, "](", url, ")"), where)) %>% 
  mutate(what = str_c(what, ", ", where)) %>%
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end))) %>% 
  select(year, what) %>% 
  kable()
```

## Teaching experience {.teaching .service .nohead}
```{r}
cv_entries %>% 
  filter(type == 'teaching') %>% 
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info),
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where))) %>% 
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end), year_begin)) %>% 
  select(year, what) %>% 
  kable()
```

# Work (non-academia)
## Selected work experience {.work .nohead .vertical-top}
```{r}
cv_entries %>% 
  filter(type == 'work') %>% 
  mutate(what = str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info)) %>% 
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end), year_begin)) %>% 
  select(year, what) %>% 
  kable()
```

## Professional development {.prof-dev .nohead}
```{r}
cv_entries %>% 
  filter(type == 'prof-dev') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year_begin, what) %>% 
  kable()
```

# Technical
## Skills {.technical .nohead}
```{r}
cv_entries %>% 
  filter(type == 'technical') %>% 
  mutate(what = str_c("- *", what, "* ", additional_info)) %>% 
  select(what) %>% 
  kable()
```

## Software development {.cv-table .nohead .vertical-top}
```{r}
cv_entries %>% 
  filter(type == 'programming') %>% 
  replace_na(list(where = "", additional_info = "")) %>% 
  mutate(what = str_c(what, ", ", where, "<br>", additional_info)) %>% 
  select(year_begin, what) %>% 
  arrange(desc(year_begin)) %>% 
  kable(align = c('l', 'l'))
```

# Personal
## Skills & volunteering {.personal .service .nohead}
```{r}
cv_entries %>%
  filter(type == 'volunteering' & professional_2_page == 'y') %>%
  mutate(what = str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where)) %>%
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end), year_begin)) %>%
  arrange(order, desc(year_end), desc(year)) %>%
  select(year, what) %>%
  kable()
```


