---
#date: "`r Sys.Date()`"
output:
  pagedown::html_paged:
    # change to true for a self-contained document, but it'll be a litte slower for Pandoc to render
    self_contained: false
    # CDS
    #css: [css/one-column-paged.css, "https://cdnjs.cloudflare.com/ajax/libs/font-awesome/4.7.0/css/font-awesome.min.css"]
    # offline
    #css: ["css/one-column-paged.css", "https://cdnjs.cloudflare.com/ajax/libs/font-awesome/4.7.0/css/font-awesome.min.css"]
    css: ["css/one-column-paged-academic.css",  "fontawesome-free-5.8.1-web/css/all.css"]
    number_sections: false
links-to-footnotes: true
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
library(googlesheets4)
library(lubridate)
gs4_deauth()

#### publications #####
# publications <- read_sheet("https://docs.google.com/spreadsheets/d/1ta71CAGkcLqm-W1UdVRA_JJSddWV2TsrRZsCnQlmOis/edit?usp=sharing",
#            sheet = "publications",
#            col_types = "c")
# publications %>% write_csv("content/publications.csv")
publications <- read_csv("content/publications.csv")

#### cv entries #####
# cv_entries <- read_sheet("https://docs.google.com/spreadsheets/d/1ta71CAGkcLqm-W1UdVRA_JJSddWV2TsrRZsCnQlmOis/edit?usp=sharing",
#            sheet = "cv_entries",
#            col_types = "c") %>%
#   mutate(year_begin = year(date_begin)) %>%
#   mutate(year_end = case_when(
#     date_end == "present" ~ date_end,
#     is.na(date_end) ~ "",
#     TRUE ~ str_sub(date_end, 1, 4)
#   ))
# cv_entries %>% write_csv("content/cv_entries.csv")
cv_entries <- read_csv("content/cv_entries.csv")
```

::: {.title-and-contact}

::: {.title}
<h1 class="title">Ulrik Lyngs</h1>
:::

::: {.contact-info}
ulrik.lyngs@cs.ox.ac.uk  \
https://ulriklyngs.com
:::

:::
<!-- TODO
1. write the opening research interests
2. ADD SECTION W/ 'Publicly available research code & data' like Matt Kay
3. reduce code redundancy
-->

## Research interests
::: {.research-interests}

::: {.spacer}
:::

::: {.interests}
**Broadly---**something about design strategies for supporting self-control over digital device use
<br>
**How I do this---**something about the Reducing Digital Distraction workshop

**I am excited** when something - it's about the limits of psychology and the capabilities of technology. 
:::
:::

<div class="cv-entries">
## Education {.education}
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = str_c("<span class='education-what'>", what, "</span>, ", where)) %>% 
  mutate(year = str_c(year_begin, " --- ", year_end)) %>% 
  select(year, what) %>% 
  kable()
```

## Awards and honours {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'awards',
         is.na(one_column_paged)) %>% 
  mutate(what = str_c("<span class='award-what'>", what, "</span>, ", where)) %>%  
  mutate(spacer = "") %>% 
  mutate(row_number = row_number()) %>% 
  mutate(year_begin = as.character(year_begin),
         year_begin = case_when(
           row_number == 1 ~ year_begin,
           year_begin == lag(year_begin) ~ "",
           year_begin != lag(year_begin) ~ year_begin
         )) %>% 
  select(year_begin, spacer, what) %>% 
  kable()
```

## Grants {.three-split}
```{r}
cv_entries %>%
  filter(type == 'minor_grants' | type == 'major_grants') %>%
  mutate(what = case_when(
    is.na(additional_info) ~ str_c("<span class='award-what'>", what, "</span> (", amount, ")<br>", where),
    !is.na(additional_info) ~ str_c("<span class='award-what'>", what, "</span> (", amount, ")<br>", where, ". ", additional_info),
  )) %>%
  mutate(row_number = row_number()) %>%
  mutate(year_begin = as.character(year_begin),
         year_begin = case_when(
           row_number == 1 ~ year_begin,
           year_begin == lag(year_begin) ~ "",
           year_begin != lag(year_begin) ~ year_begin
         )) %>%
  mutate(spacer = "") %>%
  select(year_begin, spacer, what) %>%
  kable()
```

<!-- <br class="pageBreak"> -->


## Publications {.three-split}

::: {.grid-container-publications}
<div class="conference-publication-heading">
<h3>Conference publications <br><span class="review-note">(fully reviewed, archival)</span></h3>
</div>
<div class="conference-note">
<h3>In computer science, top-tier conferences (<30% acceptance rate) are as, or more impactful than journals, see doi.org/fgjt2h</h3>
</div>
:::
```{r}
# create helper function for taking one name and replacing the first name with initial and dot
replace_first_name_with_initial_and_dot <- function(author_name) {
  str_replace(author_name, "(?<=\\S)\\S+", "\\.")
}

# create function for doing this for an entry of authors
replace_first_names_in_list_with_initial_and_dot <- function(authors){
  authors_split <- str_split(authors, ",") %>% 
    map(str_trim)
  
  authors_split[[1]] %>% map_chr(replace_first_name_with_initial_and_dot) %>% 
    paste0(collapse = ", ")
}

publications_table <- publications %>%
  filter(type == "conference paper") %>% 
  mutate(authors_full = map_chr(authors_full, replace_first_names_in_list_with_initial_and_dot)) %>% 
  arrange(desc(date)) %>%
  mutate(year = year(date)) %>% 
  mutate(citation = ifelse(!is.na(award), 
                           str_c("<span class='publication-title'>", title, "</span><br><span class='publication-authors'>", authors_full, "</span><br><span class='publication-venue'>", venue_abbrev, ": ", venue, "</span><br><i class='fas fa-award'></i> <span class='publication-award'>", award, "</span>"),
                           str_c("<span class='publication-title'>", title, "</span><br><span class='publication-authors'>", authors_full, "</span><br><span class='publication-venue'>", venue_abbrev, ": ", venue, "</span>"))) %>%
  mutate(citation = str_replace(citation, "U\\. Lyngs", "*U\\. Lyngs*"))  # make my name italic

publications_table %>%
  arrange(date) %>% 
  mutate(number = str_pad(row_number(), width = 1, side = "left", pad = "0"),
         number = str_c("C", number)) %>%
  arrange(desc(date)) %>% 
  mutate(row_number = row_number()) %>% 
  mutate(year = as.character(year),
         year = case_when(
           row_number == 1 ~ year,
           year == lag(year) ~ "",
           year != lag(year) ~ year
         )) %>% 
  select(year, number, citation) %>%
  knitr::kable() 
```

<h3>Journal publications</h3>

```{r}
publications_table <- publications %>%
  filter(type == "journal article") %>% 
  mutate(authors_full = map_chr(authors_full, replace_first_names_in_list_with_initial_and_dot)) %>% 
  arrange(desc(date)) %>%
  mutate(year = year(date)) %>% 
  mutate(citation = ifelse(!is.na(award), 
                           str_c("<span class='publication-title'>", title, "</span><br><span class='publication-authors'>", authors_full, "</span><br><span class='publication-venue'>", venue_abbrev, ": ", venue, "</span><br><i class='fas fa-award'></i> <span class='publication-award'>", award, "</span>"),
                           str_c("<span class='publication-title'>", title, "</span><br><span class='publication-authors'>", authors_full, "</span><br><span class='publication-venue'>", venue_abbrev, ": ", venue, "</span>"))) %>%
  mutate(citation = str_replace(citation, "U\\. Lyngs", "*U\\. Lyngs*"))  # make my name italic

publications_table %>%
  arrange(date) %>% 
  mutate(number = str_pad(row_number(), width = 1, side = "left", pad = "0"),
         number = str_c("J", number)) %>%
  arrange(desc(date)) %>% 
  mutate(row_number = row_number()) %>% 
  mutate(year = as.character(year),
         year = case_when(
           row_number == 1 ~ year,
           year == lag(year) ~ "",
           year != lag(year) ~ year
         )) %>% 
  select(year, number, citation) %>%
  knitr::kable() 
```


<h3>Extended abstracts and workshop papers <br><span class="review-note">(lightly reviewed)</span></h3>

```{r}
publications_table <- publications %>%
  filter(type == "extended abstract" | type == "workshop paper") %>% 
  mutate(authors_full = map_chr(authors_full, replace_first_names_in_list_with_initial_and_dot)) %>% 
  arrange(desc(date)) %>%
  mutate(year = year(date)) %>% 
  mutate(citation = ifelse(!is.na(award), 
                           str_c("<span class='publication-title'>", title, "</span><br><span class='publication-authors'>", authors_full, "</span><br><span class='publication-venue'>", venue_abbrev, ": ", venue, "</span><br><i class='fas fa-award'></i> <span class='publication-award'>", award, "</span>"),
                           str_c("<span class='publication-title'>", title, "</span><br><span class='publication-authors'>", authors_full, "</span><br><span class='publication-venue'>", venue_abbrev, ": ", venue, "</span>"))) %>%
  mutate(citation = str_replace(citation, "U\\. Lyngs", "*U\\. Lyngs*"))  # make my name italic

publications_table %>%
  arrange(date) %>% 
  mutate(number = str_pad(row_number(), width = 1, side = "left", pad = "0"),
         number = str_c("A", number)) %>% 
  arrange(desc(date)) %>% 
  mutate(row_number = row_number()) %>% 
  mutate(year = as.character(year),
         year = case_when(
           row_number == 1 ~ year,
           year == lag(year) ~ "",
           year != lag(year) ~ year
         )) %>% 
  select(year, number, citation) %>%
  knitr::kable() 
```

<!-- <br class="pageBreak"> -->

## Poster presentations {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'poster') %>%
  mutate(what = str_c("<span class='poster-location'>", where, "</span>, ", what)) %>% 
  arrange(date_begin) %>% 
  mutate(number = str_pad(row_number(), width = 1, side = "left", pad = "0"),
         number = str_c("P", number)) %>% 
  arrange(desc(date_begin)) %>% 
  mutate(row_number = row_number()) %>% 
  mutate(year_begin = as.character(year_begin),
         year_begin = case_when(
           row_number == 1 ~ year_begin,
           year_begin == lag(year_begin) ~ "",
           year_begin != lag(year_begin) ~ year_begin
         )) %>% 
  select(year_begin, number, what) %>% 
  
  kable()
```

## Talks and panels {.three-split}
::: {.conference-presentations-omitted}
All first-author conference papers listed above were also given as presentations at their respective conferences and are not listed again in this section.
:::

### Talks
```{r}
cv_entries %>% 
  filter(type == 'talk', is.na(exclude)) %>% 
  mutate(additional_info = if_else(is.na(additional_info), "", str_c(", ", additional_info))) %>% 
  mutate(what = str_c("<span class='talk-location'>", where, "</span>, ", what, additional_info)) %>% 
  arrange(date_begin) %>% 
  mutate(number = str_pad(row_number(), width = 2, side = "left", pad = "0"),
         number = str_c("T", number)) %>% 
  arrange(desc(date_begin)) %>% 
  mutate(row_number = row_number()) %>% 
  mutate(year_begin = as.character(year_begin),
         year_begin = case_when(
           row_number == 1 ~ year_begin,
           year_begin == lag(year_begin) ~ "",
           year_begin != lag(year_begin) ~ year_begin
         )) %>% 
  select(year_begin, number, what) %>% 
  kable()

```

### Discussion panels
```{r}
cv_entries %>% 
  filter(type == 'talk-panel') %>% 
  mutate(additional_info = if_else(is.na(additional_info), "", additional_info)) %>% 
  mutate(what = str_c("<span class='talk-location'>", where, "</span>, ", what, ", ",  additional_info)) %>% 
  arrange(date_begin) %>% 
  mutate(number = str_pad(row_number(), width = 1, side = "left", pad = "0"),
         number = str_c("D", number)) %>% 
  arrange(desc(date_begin)) %>% 
  mutate(row_number = row_number()) %>% 
  mutate(year_begin = as.character(year_begin),
         year_begin = case_when(
           row_number == 1 ~ year_begin,
           year_begin == lag(year_begin) ~ "",
           year_begin != lag(year_begin) ~ year_begin
         )) %>% 
  select(year_begin, number, what) %>% 
  kable()

```

### Podcasts
```{r}
cv_entries %>% 
  filter(type == 'talk-podcast') %>% 
  mutate(what = str_c("<span class='talk-location'>", where, "</span>, ", what)) %>% 
  arrange(date_begin) %>% 
  mutate(number = str_pad(row_number(), width = 1, side = "left", pad = "0"),
         number = str_c("Pod", number)) %>% 
  arrange(desc(date_begin)) %>% 
  select(year_begin, number, what) %>% 
  kable()

```

## Media coverage {.education}
```{r}
cv_entries %>% 
  filter(type == 'media') %>%
  select(year_begin, what) %>% 
  kable()
```

<!-- <br class="pageBreak"> -->

## Teaching experience {.education}
```{r}
cv_entries %>% 
  filter(type == 'teaching') %>% 
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='work-title'>", what, "</span>, ", where, "<br>", additional_info),
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where))) %>% 
  mutate(year = ifelse((is.na(year_end) | year_begin == year_end), year_begin, str_c(year_begin, " --- ", year_end))) %>% 
  select(year, what) %>% 
  kable()
```

## Service {.education}
```{r}
cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(year_end = ifelse(year_end == "present", "", year_end)) %>% 
  mutate(where = ifelse(!is.na(url), str_c("[", where, "](", url, ")"), where)) %>% 
  mutate(what = str_c("<span class='service-what'>", what, "</span>, ", where)) %>%
  mutate(year = ifelse(!(year_end == year_begin), 
                       str_c(year_begin, " --- ", year_end), 
                       year_begin)) %>% 
  select(year, what) %>% 
  kable()
```

## Selected work experience {.education}
```{r}
cv_entries %>% 
  filter(type == 'work', is.na(one_column_paged)) %>% 
  mutate(additional_info = replace_na(additional_info, "")) %>% 
  mutate(what = str_c("<span class='work-title'>", what, "</span>, ", where, "<br>", additional_info)) %>% 
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end), year_begin)) %>% 
  select(year, what) %>% 
  kable()
```


## Professional development {.education}
```{r}
cv_entries %>% 
  filter(type == 'prof-dev') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year_begin, what) %>% 
  kable()
```

<br class="pageBreak">

## R packages {.education}
```{r}
cv_entries %>% 
  filter(type == 'programming' & is.na(exclude)) %>% 
  replace_na(list(where = "", additional_info = "")) %>% 
  mutate(what = str_c(what, ", ", where, "<br>", additional_info)) %>% 
  arrange(desc(year_begin)) %>% 
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end), year_begin)) %>% 
  mutate(row_number = row_number()) %>% 
  mutate(year = as.character(year),
         year = case_when(
           row_number == 1 ~ year,
           year_begin == lag(year) ~ "",
           year_begin != lag(year) ~ year
         )) %>% 
  select(year, what) %>% 
  kable(align = c('l', 'l'))
```

<!-- <br class="pageBreak"> -->

## Personal skills & volunteering {.education}
```{r}
cv_entries %>%
  filter(type == 'volunteering' & professional_2_page == 'y') %>%
  mutate(what = str_c("<span class='work-title'>", what, "</span>, ", where)) %>%
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%
  mutate(year = ifelse(!is.na(year_end), 
                       str_c(year_begin, " --- ", year_end), 
                       year_begin)) %>%
  arrange(order, desc(year_end), desc(year)) %>%
  select(year, what) %>%
  kable()
```

<br class="pageBreak">

<!-- close 'cv-entries' div -->
</div>
# Links
