---
title: "Ulrik Lyngs <br> Curriculum vitae"
#date: "`r Sys.Date()`"
output:
  pagedown::html_paged:
    # change to true for a self-contained document, but it'll be a litte slower for Pandoc to render
    self_contained: false
    css: [one-column.css, default-page.css, "https://use.fontawesome.com/releases/v5.7.2/css/all.css"]
    #template: ul_template.html
    #template: paged.html
    number_sections: false
links-to-footnotes: true
params:
  include_all: true #set to false for short 2-column version
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)


#### create publications table #####
publications <- readxl::read_xlsx("../cv_data/publications.xlsx")

#### create education table #####
cv_entries <- readxl::read_xlsx("../cv_data/cv_entries.xlsx")

```

<div class="grid-container">
```{block type="col-6 grid-item", echo=TRUE}
## Personal summary {.summary}
I am a cognitive psychologist-turned-computer scientist. I am passionate about applying insights from the behavioural neurosciences to design digital technology that is sensitive to human limitations and biases, particularly in relation to attention and self-regulation.

```

```{block type='col-6 grid-item', echo=TRUE}
## Contact information {.box}
<div class="info-box">

| Center | Left |
|:------:|:-----|
| <i class="fas fa-map-marker-alt"></i>|Department of Computer Science,\
University of Oxford, Oxford, UK|
| <i class="fas fa-mobile-alt"></i> | +44 (0)7472 185588 |
| <i class="fas fa-envelope"></i> | ulrik.lyngs\@cs.ox.ac.uk |
| <i class="fas fa-globe"></i> | [ulriklyngs.com](https://ulriklyngs.com) |

 
</div>

```

</div>

## Education {.education .nohead}
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year, what) %>% 
  kable()
```


## Grants and Awards {.grants .nohead}
```{r}
cv_entries %>% 
  filter(type == 'grants_and_awards') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year, what) %>% 
  kable()
```

`r ifelse(params$include_all, "## Publications {.publications .nohead}", "## Selected Publications {.publications .nohead}")`
```{r}
publications_table <- publications %>%
  arrange(desc(year), type) %>%
  mutate(author_year = str_c(authors, " (", year, "). ")) %>%
  #mutate(author_year = str_c("*", authors, " (", year, ")*. ")) %>%  #italicise authors and year
  mutate(title = ifelse(!is.na(url), str_c("[", title, "](", url, ")"), title)) %>% #turn title into link
  #mutate(title = str_c("<span style='text-decoration: underline'>", title, "</span>")) %>% #underline title
  mutate(citation = ifelse(!is.na(award), 
                           str_c(author_year, title, venue, "<i class='fas fa-award'></i><em>", award, "</em>", sep = " "),
                           str_c(author_year, title, venue, sep = " "))) %>%
  mutate(citation = str_replace(citation, "Lyngs, U.", "__Lyngs, U.__")) # make my name bold

if (params$include_all) {
  publications_table %>%
    select(type, citation) %>%
    knitr::kable()
} else {
  publications_table %>%
    filter(!is.na(short_cv)) %>%
    select(citation) %>%
    knitr::kable()
}
```

`r ifelse(params$include_all, "## Talks {.talks .nohead}", "## Selected talks {.talks .nohead}")`
```{r}
cv_entries %>% 
  filter(type == 'talk') %>% 
  mutate(what = str_c("*", what, "*, ", where)) %>% 
  select(year, what) %>% 
  kable()
```

`r ifelse(params$include_all, "## Poster presentations {.posters .nohead .vertical-top .smaller-font}", "## Selected poster presentations {.posters .nohead .vertical-top .smaller-font}")`
```{r}
cv_entries %>% 
  filter(type == 'poster') %>%
  mutate(what = str_c("*", what, "*, ", where)) %>% 
  select(year, what) %>% 
  arrange(desc(year)) %>% 
  kable()
```

## Media coverage {.media .nohead}
```{r}
cv_entries %>% 
  filter(type == 'media') %>%
  select(year, what) %>% 
  kable()
```

## Service {.service .nohead}
```{r}
cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(where = ifelse(!is.na(url), str_c("[", where, "](", url, ")"), where)) %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year, what) %>% 
  kable()
```

## Professional development {.prof-dev .nohead}
```{r}
cv_entries %>% 
  filter(type == 'prof-dev') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year, what) %>% 
  kable()
```

<br class='pageBreak'>

## Selected work experience {.work .nohead .vertical-top}
```{r}
cv_entries %>% 
  filter(type == 'work') %>% 
  mutate(what = str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info)) %>% 
  select(year, what) %>% 
  kable()
```


## Technical skills {.technical .nohead}
```{r}
cv_entries %>% 
  filter(type == 'technical') %>% 
  mutate(what = str_c("- *", what, "* ", additional_info)) %>% 
  select(what) %>% 
  kable()
```

<br class='pageBreak'>

### Links