---
#date: "`r Sys.Date()`"
output:
  pagedown::html_paged:
    css: ["css/one-column-paged-academic.css",  "https://use.fontawesome.com/releases/v5.7.2/css/all.css"]
    number_sections: false
links-to-footnotes: true
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
library(lubridate)

######## CREATE HELPER FUNCTIONS
# function which takes a name and replaces the first name with initial and dot
replace_first_name_with_initial_and_dot <- function(author_name) {
  str_replace(author_name, "(?<=\\S)\\S+", "\\.")
}

# function for doing this for an entry with a number of authors
replace_first_names_in_list_with_initial_and_dot <- function(authors){
  authors_split <- str_split(authors, ",") %>% 
    map(str_trim)
  
  authors_split[[1]] %>% map_chr(replace_first_name_with_initial_and_dot) %>% 
    paste0(collapse = ", ")
}

# function for adding leading zero's when there's more than 10 entries
padding_function <- function(cv_entries_tibble, letter_to_pad){
  if(nrow(cv_entries_tibble) > 9){
    cv_entries_tibble %>% 
      arrange(date) %>%
  mutate(number = str_pad(row_number(), width = 2, side = "left", pad = "0"),
         number = str_c(letter_to_pad, number)) %>%
  arrange(desc(date))
  } else {
    cv_entries_tibble %>% 
      arrange(date) %>%
  mutate(number = str_pad(row_number(), width = 1, side = "left", pad = "0"),
         number = str_c(letter_to_pad, number)) %>%
  arrange(desc(date))
  }
}

# function for making a year blank when it's the same as the one preceding it
blank_year_when_repeated <- function(cv_entry_tibble){
  cv_entry_tibble %>% 
    mutate(row_number = row_number()) %>% 
    mutate(year_begin = as.character(year_begin),
           year_begin = case_when(
             row_number == 1 ~ year_begin,
             year_begin == lag(year_begin) ~ "",
             year_begin != lag(year_begin) ~ year_begin
           ))
}


####### READ IN DATA
#### publications #####
publications <- read_csv("_content/publications.csv") %>% 
  mutate(authors_full = map_chr(authors_full, replace_first_names_in_list_with_initial_and_dot)) %>% 
  mutate(authors_full = str_replace(authors_full, "U\\. Lyngs", "*U\\. Lyngs*")) %>%   # make my name italic
  mutate(year_begin = year(date))
  
#### cv entries #####
cv_entries <- read_csv("_content/cv_entries.csv") %>% 
  mutate(year_begin = year(date_begin)) %>%
  mutate(year_end = case_when(
    date_end == "present" ~ date_end,
    !is.na(date_end) ~ str_sub(date_end, 1, 4),
    is.na(date_end) ~ date_end
  )) %>%
  mutate(year = ifelse((is.na(year_end) | year_begin == year_end),
                      year_begin,
                      str_c(year_begin, " --- ", year_end)))

```

:::::: {.title-and-contact}

::: {.title}
<h1 class="title">Ulrik Lyngs</h1>
:::

::: {.contact-info}
ulrik.lyngs@cs.ox.ac.uk  \
https://ulriklyngs.com
:::

::::::

## Research summary
:::::: {.research-interests}

::: {.spacer}
:::

::: {.interests}
**Aims---**to develop and evaluate design patterns that help people exercise self-control over their use of smartphones and laptops.
<br>
**Methods---**controlled studies, user surveys, interviews, co-design workshops, web scraping, behaviour logging.

**I am passionate about** open and transparent research. 
Since 2018, I have shared materials, analysis scripts, and data for all my work, and written my papers as reproducible documents in [R Markdown](https://rmarkdown.rstudio.com).
:::
::::::

<div class="cv-entries">
## Education
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(additional_info = ifelse(str_detect(additional_info, "and"), 
                                  str_c("<span class='supervisor'>Supervisors: </span>", additional_info),
                                  str_c("<span class='supervisor'>Supervisor: </span>", additional_info))) %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span>, ", 
                      where, "<br>", additional_info,
                      "<br><span class='thesis-title'>Thesis: </span>", additional_info2)) %>% 
  select(year, what) %>% 
  kable()
```

## Awards & honours
```{r}
cv_entries %>% 
  filter(type == 'awards') %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span>, ", where)) %>%  
  blank_year_when_repeated() %>% 
  select(year_begin, what) %>% 
  kable()
```

<br class="pageBreak">

## Grants
```{r}
cv_entries %>%
  filter(type == 'minor_grants' | type == 'major_grants') %>%
  mutate(what = case_when(
    is.na(additional_info) ~ str_c("<span class='cv-entry-title'>", what, "</span> (", additional_info2, "), ", where),
    !is.na(additional_info) ~ str_c("<span class='cv-entry-title'>", what, "</span> (", additional_info2, "), ", where, ".<br> ", additional_info),
  )) %>%
  blank_year_when_repeated() %>% 
  select(year, what) %>%
  kable()
```


## Publications {.three-split}

:::::: {.grid-container-publications}
::: {.conference-publication-heading}
<h3>Conference publications <br><span class="review-note">(fully reviewed, archival)</span></h3>
:::
::: {.conference-note}
<h3>In computer science, top-tier conferences (<30% acceptance rate) are as, or more impactful than journals, see doi.org/fgjt2h</h3>
:::
::::::


```{r}
publications %>%
  filter(type == "conference paper") %>% 
  # insert appropriate icon for best paper awards
  mutate(citation = case_when(
    !is.na(award) & str_detect(award, "honourable") ~ str_c("<span class='cv-entry-title'>", title, "</span><br><span class='publication-authors'>", authors_full, "</span><br><span class='publication-venue'>", venue_abbrev, ": ", venue, "</span><br><i class='fas fa-award'></i> <span class='publication-award'>", award, "</span>"),
    !is.na(award) ~ str_c("<span class='cv-entry-title'>", title, "</span><br><span class='publication-authors'>", authors_full, "</span><br><span class='publication-venue'>", venue_abbrev, ": ", venue, "</span><br><i class='fa fa-trophy'></i> <span class='publication-award'>", award, "</span>"),
    TRUE ~ str_c("<span class='cv-entry-title'>", title, "</span><br><span class='publication-authors'>", authors_full, "</span><br><span class='publication-venue'>", venue_abbrev, ": ", venue, "</span>")
    )) %>% 
  # number entries with a prefix
  padding_function(., "C") %>% 
  blank_year_when_repeated() %>%
  select(year_begin, number, citation) %>%
  knitr::kable()
```

<!-- <br class="pageBreak"> -->
<h3>Journal articles <span class="review-note">(fully reviewed, archival)</span></h3>

```{r}
publications %>%
  filter(type == "journal article") %>% 
  mutate(citation = str_c("<span class='cv-entry-title'>", title, "</span><br><span class='publication-authors'>", authors_full, "</span><br><span class='publication-venue'>", venue_abbrev, ": ", venue, "</span>")) %>% 
  padding_function(., "J") %>% 
  blank_year_when_repeated() %>%
  select(year_begin, number, citation) %>%
  knitr::kable()
```


<h3>Extended abstracts and workshop papers <br><span class="review-note">(lightly reviewed)</span></h3>

```{r}
publications %>%
  filter(type == "extended abstract" | type == "workshop paper") %>% 
  mutate(citation = str_c("<span class='cv-entry-title'>", title, "</span><br><span class='publication-authors'>", authors_full, "</span><br><span class='publication-venue'>", venue_abbrev, ": ", venue, "</span>")) %>%
  padding_function(., "A") %>% 
  blank_year_when_repeated() %>%
  select(year_begin, number, citation) %>%
  knitr::kable()
```

<!-- <br class="pageBreak"> -->

## Poster presentations {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'poster') %>%
  mutate(what = str_c("<span class='cv-entry-title'>", where, "</span>, ", what)) %>% 
  mutate(date = date_begin) %>%
  padding_function(., "P") %>% 
  blank_year_when_repeated() %>% 
  select(year_begin, number, what) %>% 
  knitr::kable()
```

## Talks and panels {.three-split}
::: {.conference-presentations-omitted}
All first-authored conference publications listed above were also given as presentations at their respective conferences and are not listed again in this section.
:::

### Talks
```{r}
cv_entries %>% 
  filter(type == 'talk', is.na(exclude)) %>% 
  mutate(additional_info = if_else(is.na(additional_info), "", str_c(", ", additional_info))) %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", where, "</span>, ", what, additional_info)) %>% 
  mutate(date = date_begin) %>% 
  padding_function(., "T") %>% 
  blank_year_when_repeated() %>% 
  select(year_begin, number, what) %>% 
  knitr::kable()

```

### Discussion panels
```{r}
cv_entries %>% 
  filter(type == 'talk-panel') %>% 
  mutate(additional_info = if_else(is.na(additional_info), "", additional_info)) %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", where, "</span>, ", what, ", ",  additional_info)) %>% 
  mutate(date = date_begin) %>% 
  padding_function(., "D") %>% 
  blank_year_when_repeated() %>% 
  select(year_begin, number, what) %>% 
  knitr::kable()

```

<!-- <br class="pageBreak"> -->

## Podcasts {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'talk-podcast') %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", where, "</span>, ", what)) %>% 
  mutate(date = date_begin) %>% 
  padding_function(., "Pod") %>% 
  blank_year_when_repeated() %>% 
  select(year_begin, number, what) %>% 
  knitr::kable()

```

## Press
```{r}
cv_entries %>% 
  filter(type == 'media') %>%
  select(year_begin, what) %>% 
  kable()
```

<!-- <br class="pageBreak"> -->

## Teaching experience
```{r}
cv_entries %>% 
  filter(type == 'teaching') %>% 
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='cv-entry-title'>", what, "</span>, ", where, "<br>", additional_info),
    str_c("<span class='cv-entry-title'>", what, "</span><br>", where))) %>% 
  select(year, what) %>% 
  kable()
```

## Service
```{r}
cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(where = ifelse(!is.na(url), str_c("[", where, "](", url, ")"), where)) %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span>, ", where)) %>%
  select(year, what) %>% 
  kable()
```

<!-- <br class="pageBreak"> -->

## Selected work experience
```{r}
cv_entries %>% 
  filter(type == 'work', is.na(one_column_paged)) %>% 
  mutate(additional_info = replace_na(additional_info, "")) %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span>, ", where, "<br>", additional_info)) %>% 
  select(year, what) %>% 
  kable()
```


## Professional development
```{r}
cv_entries %>% 
  filter(type == 'prof-dev') %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span>, ", where)) %>% 
  select(year_begin, what) %>% 
  kable()
```

<!-- <br class="pageBreak"> -->

## R packages
```{r}
cv_entries %>% 
  filter(type == 'programming' & is.na(exclude)) %>% 
  replace_na(list(where = "", additional_info = "")) %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span>, ", where, "<br>", additional_info)) %>% 
  arrange(desc(year_begin)) %>% 
  mutate(row_number = row_number()) %>% 
  select(year, what) %>% 
  kable()
```

<!-- <br class="pageBreak"> -->

## Personal skills & volunteering {.packages}
```{r}
cv_entries %>%
  filter(type == 'volunteering') %>%
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span>, ", where)) %>%
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%
  arrange(order, desc(year_end), desc(year)) %>%
  select(year, what) %>%
  kable()
```

<br class="pageBreak">

<!-- close 'cv-entries' div -->
</div>
# Links
