---
output:
  pagedown::html_paged:
    css: ["css/one-column-paged-academic.css",  "https://use.fontawesome.com/releases/v5.7.2/css/all.css"]
    number_sections: false
links-to-footnotes: true
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(lubridate)
library(glue)

######## CREATE HELPER FUNCTIONS
# function which takes a name and replaces the first name with initial and dot
replace_first_name_with_initial_and_dot <- function(author_name) {
  str_replace(author_name, "(?<=\\S)\\S+", "\\.")
}

# function for doing this for an entry with a number of authors
replace_first_names_in_list_with_initial_and_dot <- function(authors){
  authors_split <- str_split(authors, ",") %>% 
    map(str_trim)
  
  authors_split[[1]] %>% map_chr(replace_first_name_with_initial_and_dot) %>% 
    paste0(collapse = ", ")
}

# function for adding leading zero's when there's more than 10 entries
padding_function <- function(cv_entries_tibble, letter_to_pad){
  if(nrow(cv_entries_tibble) > 9){
    cv_entries_tibble %>% 
      arrange(date) %>%
  mutate(number = str_pad(row_number(), width = 2, side = "left", pad = "0"),
         number = str_c(letter_to_pad, number)) %>%
  arrange(desc(date))
  } else {
    cv_entries_tibble %>% 
      arrange(date) %>%
  mutate(number = str_pad(row_number(), width = 1, side = "left", pad = "0"),
         number = str_c(letter_to_pad, number)) %>%
  arrange(desc(date))
  }
}

# function for making a year blank when it's the same as the one preceding it
blank_year_when_repeated <- function(cv_entry_tibble){
  cv_entry_tibble %>% 
    mutate(row_number = row_number()) %>% 
    mutate(year = as.character(year),
           year = case_when(
             row_number == 1 ~ year,
             year == lag(year) ~ "",
             year != lag(year) ~ year
           )) %>% 
    select(-row_number)
}


####### READ IN DATA
#### publications #####
publications <- read_csv("_content/publications.csv") %>% 
  mutate(authors_full = map_chr(authors_full, replace_first_names_in_list_with_initial_and_dot)) %>% 
  mutate(authors_full = str_replace(authors_full, "U\\. Lyngs", "*U\\. Lyngs*")) %>%    # make my name italic
  mutate(year = year(date)) %>% 
  mutate(venue_abbrev = if_else(!is.na(venue_abbrev), str_c(venue_abbrev, ": "), "")) # make the abbrevation an empty string if NA; add a colon and a space after if it if there is one

#### cv entries #####
cv_entries <- read_csv("_content/cv_entries.csv") %>% 
  mutate(year = year(date)) %>%
  mutate(year_end = case_when(
    date_end == "present" ~ date_end,
    !is.na(date_end) ~ str_sub(date_end, 1, 4),
    is.na(date_end) ~ date_end
  )) %>%
  mutate(year = ifelse((is.na(year_end) | year == year_end),
                      year,
                      str_c(year, " --- ", year_end)))

```


```{css}
:root{
  --last-updated: " \00a0 \00a0 \00a0 \00a0 Last updated: March 2022";
}
```



:::::: {.title-and-contact}

::: {.title}
<h1 class="title">Ulrik Lyngs</h1>
:::

::: {.contact-info}
ulrik.lyngs@cs.ox.ac.uk  \
https://ulriklyngs.com
:::

::::::

## Research summary
:::::: {.research-interests}

::: {.spacer}
:::

::: {.interests}
**Aims---**to develop and evaluate design patterns that help people self-regulate their use of smartphones and laptops.
<br>
**Methods---**controlled studies, user surveys, interviews, co-design workshops, web scraping, behaviour logging.

**I am passionate about** open and transparent research. 
Since 2018, I have shared materials, analysis scripts, and data for all my first-authored work, and written my papers as reproducible documents in [R Markdown](https://rmarkdown.rstudio.com).
:::
::::::

<div class="cv-entries">
## Research positions
```{r}
cv_entries %>% 
  filter(type == 'research_positions', is.na(exclude)) %>%
  mutate(what = glue("<span class='cv-entry-title'>{what}</span><br>",
                     "{where}"
                     )) %>% 
  select(year, what) %>% 
  kable()
```



## Education
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>", 
                      "{additional_info}<br>",
                      "<span class='thesis-title'>{additional_info2}</span>")) %>% 
  select(year, what) %>% 
  kable()
```

## Major grants and funding
```{r}
cv_entries %>%
  filter(type == 'major_grants') %>%
  mutate(what = if_else(is.na(additional_info),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}"),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}.<br>{additional_info}"))) %>%
  select(year, what) %>%
  kable()
```

## Awards & honours
```{r}
cv_entries %>% 
  filter(type == 'awards') %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) %>%  
  blank_year_when_repeated() %>% 
  select(year, what) %>% 
  kable()
```


## Publications {.three-split}

:::::: {.grid-container-publications}
::: {.conference-publication-heading}
<h3>Conference publications <br><span class="review-note">(fully reviewed, archival)</span></h3>
:::
::: {.conference-note}
<h3>In computer science, top-tier conferences (<30% acceptance rate) are as, or more impactful than journals, see doi.org/fgjt2h</h3>
:::
::::::


```{r}
publications %>%
  filter(type == "conference paper") %>% 
  # insert appropriate icon for paper awards (and start with a line break)
  mutate(award = case_when(
    !is.na(award) & str_detect(award, "honourable") ~ glue("<br><i class='fas fa-award'></i> <span class='publication-award'>{award}</span>"),
    !is.na(award) ~ glue("<br><i class='fa fa-trophy'></i> <span class='publication-award'>{award}</span>"),
    TRUE ~ ""
  )) %>% 
  # create citations
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors_full}</span><br>",
                         "<span class='publication-venue'>{venue_abbrev}{venue}</span>{award}")) %>% 
  # number entries with a prefix
  padding_function(., "C") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, citation) %>%
  knitr::kable()
```

<!-- <br class="pageBreak"> -->
<h3>Journal articles <span class="review-note">(fully reviewed, archival)</span></h3>

```{r}
publications %>%
  filter(type == "journal article") %>% 
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors_full}</span><br>",
                         "<span class='publication-venue'>{venue_abbrev}{venue}</span>")) %>% 
  padding_function(., "J") %>% 
  blank_year_when_repeated() %>%
  select(year, number, citation) %>%
  knitr::kable()
```

<h3>Book chapters</h3>

```{r}
publications %>% 
  filter(type == "book chapter") %>% 
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors_full}</span><br>",
                         "<span class='publication-venue'>{venue_abbrev}: {venue}</span>")) %>%
  padding_function(., "B") %>% 
  blank_year_when_repeated() %>%
  select(year, number, citation) %>%
  knitr::kable()

```

<h3>Extended abstracts and workshop papers <br><span class="review-note">(lightly reviewed)</span></h3>

```{r}
publications %>%
  filter(type == "extended abstract" | type == "workshop paper") %>% 
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors_full}</span><br>",
                         "<span class='publication-venue'>{venue_abbrev} {venue}</span>")) %>%
  padding_function(., "A") %>% 
  blank_year_when_repeated() %>%
  select(year, number, citation) %>%
  knitr::kable()

```

## Publicly available research code & data
```{r}
pubs_w_number <- publications %>% 
  select(type, authors_full, date, title, materials) %>% 
  mutate(inclusive_type = if_else(type == "workshop paper" | type == "extended abstract", "abstract", type)) %>% 
  group_by(inclusive_type) %>% 
  arrange(date) %>% 
  mutate(number = row_number(),
         number = case_when(
           inclusive_type == "conference paper" ~ glue("[C{number}]"),
           inclusive_type == "journal article" ~ glue("[J{number}]"),
           inclusive_type == "abstract" ~ glue("[A{number}]"),
           TRUE ~ ""
         ))

public_code <- cv_entries %>% 
  filter(type == 'open_research' & is.na(exclude)) %>% 
  select(what, additional_info) %>% 
  rename(title = additional_info) %>% 
  left_join(pubs_w_number)

public_code %>% 
  mutate(year = year(date)) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what} {number}</span><br>", 
                      "{authors_full}<br>",
                      "{materials}")) %>% 
  arrange(desc(date)) %>% 
  select(year, what) %>% 
  blank_year_when_repeated() %>% 
  kable()
```

## Research dissemination
### Press
```{r}
cv_entries %>% 
  filter(type == 'media') %>%
  select(year, what) %>% 
  kable()
```

### Podcasts {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'talk-podcast') %>% 
  mutate(what_translation = ifelse(!is.na(what_translation), str_c("(", what_translation, ")"), what_translation)) %>% 
  replace_na(list(what_translation = "")) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what} <span class='cv-entry-translation'>{what_translation}</span>")) %>%
  padding_function(., "Pod") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, what) %>% 
  knitr::kable()

```


### Talks {.three-split}

::: {.conference-presentations-omitted}
All first-authored conference publications listed above were also presented as talks at their respective conferences and are not listed again in this section.
:::

```{r}
cv_entries %>% 
  filter(type == 'talk', is.na(exclude)) %>% 
  # add commas as appropriate
  mutate(where = if_else(!is.na(where) & !is.na(institution), glue(", {where}"), where),
         department = if_else(!is.na(department), glue(", {department}"), department),
         slides = if_else(!is.na(slides), glue("<a href={slides}>Slides</a>"), ""),
         video = if_else(!is.na(video), glue("<a href={video}>Video</a>"), "")) %>%
  mutate(additional_info = if_else(!is.na(additional_info), glue(", {additional_info}"), "")) %>% 
  mutate(what_translation = ifelse(!is.na(what_translation), str_c("(", what_translation, ")"), what_translation)) %>% 
  replace_na(list(what_translation = "")) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{institution}{where}</span>{department}{additional_info}<br>",
                      "<span style='display:inline-block;' class='talk-title'>{what}</span> <span class='cv-entry-translation'>{what_translation}</span>", 
                     .na = "")) %>% 
  padding_function(., "T") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, what) %>% 
  knitr::kable()


```

### Discussion panels {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'talk-panel') %>%
  mutate(additional_info = if_else(is.na(additional_info), "", additional_info)) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what},  {additional_info}")) %>%
  padding_function(., "D") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, what) %>% 
  knitr::kable()

```

<br class="pageBreak">

### Poster presentations {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'poster') %>%
  mutate(where = if_else(!is.na(where) & !is.na(institution), glue(", {where}"), where),
         department = if_else(!is.na(department), glue(", {department}"), department)) %>%
  mutate(additional_info = if_else(!is.na(additional_info), glue(", {additional_info}"), "")) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{institution}{where}</span>{department}{additional_info}<br>",
                      "<span style='display:inline-block;' class='talk-title'>{what}</span>", 
                     .na = "")) %>% 
  padding_function(., "P") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, what) %>%
  knitr::kable()



```

### Blog posts {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'pop-writing') %>%
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what}")) %>%
  padding_function(., "B") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, what) %>% 
  knitr::kable()
```


<br class="pageBreak">

## Teaching experience
```{r}
cv_entries %>% 
  filter(type == 'teaching') %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>",
         "{additional_info}")) %>% 
  select(year, what) %>% 
  kable()
```

<!-- <br class="pageBreak"> -->

## Software
### R packages
```{r}
cv_entries %>% 
  filter(type == 'software-rstats' & is.na(exclude)) %>% 
  replace_na(list(where = "", additional_info = "")) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) %>%
  arrange(desc(year)) %>% 
  mutate(row_number = row_number()) %>% 
  select(year, what) %>% 
  kable()
```

### Apps
```{r}
cv_entries %>% 
  filter(type == 'software-browser-extensions' & is.na(exclude)) %>% 
  replace_na(list(where = "", additional_info = "")) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) %>%
  arrange(desc(year)) %>% 
  mutate(row_number = row_number()) %>% 
  select(year, what) %>% 
  kable()
```


## Service
```{r}
cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(where = if_else(!is.na(url), glue("[{where}]({url})"), where)) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span> {where}")) %>%
  arrange(desc(date_end), desc(date)) %>% 
  select(year, what) %>% 
  kable()
```


<!-- <br class="pageBreak"> -->

## Selected work experience
```{r}
cv_entries %>% 
  filter(type == 'work', is.na(one_column_paged)) %>% 
  mutate(additional_info = replace_na(additional_info, "")) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>",
                     "{additional_info}")) %>% 
  select(year, what) %>% 
  kable()
```

<br class="pageBreak">

## Professional development
```{r}
cv_entries %>% 
  filter(type == 'prof-dev') %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) %>%
  select(year, what) %>% 
  kable()
```

## Minor grants and funding
```{r}
cv_entries %>%
  filter(type == 'minor_grants') %>%
  mutate(what = if_else(!is.na(additional_info),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}.<br> ", 
                             "{additional_info}"),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}"))) %>%
  blank_year_when_repeated() %>% 
  select(year, what) %>%
  kable()
```

<!-- <br class="pageBreak"> -->

## Personal skills & volunteering {.packages}
```{r}
cv_entries %>%
  filter(type == 'volunteering') %>%
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) %>%
  mutate(what = if_else(!is.na(additional_info), glue("{what}<br>{additional_info}"), what)) %>%
  arrange(desc(date), desc(date_end)) %>% 
  select(year, what) %>%
  kable()
```

<!-- <br class="pageBreak"> -->

<!-- close 'cv-entries' div -->
</div>

<br class="pageBreak">

# Links
