---
title: "Ulrik Lyngs <br> Curriculum vitae"
output:
  pagedown::html_paged:
    css: ["css/one-column-paged.css", "https://use.fontawesome.com/releases/v5.7.2/css/all.css"]
    number_sections: false
links-to-footnotes: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
library(lubridate)

#### publications #####
publications <- read_csv("_content/publications.csv")

#### cv entries #####
cv_entries <- read_csv("_content/cv_entries.csv") %>% 
  mutate(year_begin = year(date)) %>%
  mutate(year_end = case_when(
    date_end == "present" ~ date_end,
    !is.na(date_end) ~ str_sub(date_end, 1, 4),
    is.na(date_end) ~ date_end
  )) %>%
  mutate(year = ifelse((is.na(year_end) | year_begin == year_end),
                      year_begin,
                      str_c(year_begin, " --- ", year_end)))

```

<div class="grid-container"> 
<!-- top row -->
```{block type="grid-item", echo=TRUE}
## Personal summary {.summary}
I am a computer scientist and cognitive psychologist, working on design patterns that support self-control over digital device use.
I am passionate about open science and teach workshops on reproducible research with R and R Markdown.
```

```{block type='grid-item', echo=TRUE}
## Contact information {.box}
<div class="info-box">

| Center | Left |
|:------:|:-----|
| <i class="fas fa-map-marker-alt"></i>|Department of Computer Science,\
University of Oxford, UK|
| <i class="fa fa-envelope"></i> | ulrik.lyngs\@cs.ox.ac.uk |
| <i class="fas fa-globe"></i> | [ulriklyngs.com](https://ulriklyngs.com) |
| <i class="fab fa-github"></i> | [ulyngs](https://github.com/ulyngs) |
 
</div>
```

</div>

## Education {.education .nohead .set-width}
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  mutate(year = str_c(year_begin, " --- ", year_end)) %>% 
  select(year, what) %>% 
  kable()
```

## Awards and honours {.grants .nohead .set-width}
```{r}
cv_entries %>% 
  filter(type == 'awards',
         is.na(one_column_paged)) %>% 
  mutate(what = str_c(what, ", ", where)) %>%  
  select(year_begin, what) %>% 
  kable()
```

## Grants {.grants .nohead .set-width}
```{r}
cv_entries %>% 
  filter(type == 'minor_grants' | type == 'major_grants', is.na(one_column_paged)) %>% 
  mutate(what = if_else(!is.na(additional_info),
                        str_c(what, " (", additional_info, "), ", where),
                        str_c(what, ", ", where))) %>% 
  select(year_begin, what) %>% 
  kable()
```

<!-- <br class="pageBreak"> -->

## Publications {.nohead .publications .set-width}
```{r}
publications_table <- publications %>%
  arrange(desc(date), type) %>%
  mutate(author_year = str_c(authors_full, " (", year(date), "). ")) %>%
  mutate(title = ifelse(!is.na(url), str_c("[", title, "](", url, ")"), title)) %>% #turn title into link
  mutate(citation = ifelse(!is.na(award), 
                           str_c(author_year, title, venue, "<i class='fas fa-award'></i><em>", award, "</em>", sep = " "),
                           str_c(author_year, title, venue, sep = " "))) %>%
  mutate(citation = str_replace(citation, "Ulrik Lyngs", "__Ulrik Lyngs__")) # make my name bold

publications_table %>%
  filter(type != "master's thesis") %>% 
  select(type, citation) %>%
  knitr::kable()
```

<!-- <br class="pageBreak"> -->

## Talks {.nohead .talks .set-width}
```{r}
cv_entries %>% 
  filter(type == 'talk') %>% 
  mutate(what = str_c("*", what, "*, ", where)) %>% 
  select(year_begin, what) %>% 
  kable()

```

## Poster presentations {.nohead .posters .set-width}
```{r}
cv_entries %>% 
  filter(type == 'poster') %>%
  mutate(what = str_c("*", what, "*, ", where)) %>% 
  select(year_begin, what) %>% 
  arrange(desc(year_begin)) %>% 
  kable()
```

## Media coverage {.media .nohead .set-width}
```{r}
cv_entries %>% 
  filter(type == 'media') %>%
  select(year_begin, what) %>% 
  kable()
```

<br class="pageBreak">

## Teaching experience {.teaching .nohead .set-width}
```{r}
cv_entries %>% 
  filter(type == 'teaching') %>% 
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info),
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where))) %>% 
  select(year, what) %>% 
  kable()
```

## Service {.service .nohead .set-width}
```{r}
cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(year_end = ifelse(year_end == "present", "", year_end)) %>% 
  mutate(where = ifelse(!is.na(url), str_c("[", where, "](", url, ")"), where)) %>% 
  mutate(what = str_c(what, ", ", where)) %>%
  select(year, what) %>% 
  kable()
```

## Selected work experience {.work .nohead .vertical-top .set-width}
```{r}
cv_entries %>% 
  filter(type == 'work', is.na(one_column_paged)) %>% 
  mutate(additional_info = replace_na(additional_info, "")) %>% 
  mutate(what = str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info)) %>% 
  select(year, what) %>% 
  kable()
```


## Professional development {.prof-dev .nohead .set-width}
```{r}
cv_entries %>% 
  filter(type == 'prof-dev') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year_begin, what) %>% 
  kable()
```

## Technical skills {.technical .nohead .set-width}
```{r}
cv_entries %>% 
  filter(type == 'technical') %>% 
  mutate(icon = case_when(
    str_detect(what, "data analysis") ~ "fa-bar-chart",
    str_detect(what, "research") ~ "fa-flask",
    str_detect(what, "Web") ~ "fa-laptop"
  )) %>% 
  mutate(icon = str_c("<i class='fa fa-lg ", icon, "'></i>")) %>% 
  mutate(what = str_c(what, " ", additional_info)) %>% 
  select(icon, what) %>% 
  kable(escape = FALSE)
```

## Software development {.nohead .vertical-top .set-width}
```{r}
cv_entries %>% 
  filter(type == 'programming') %>% 
  replace_na(list(where = "", additional_info = "")) %>% 
  mutate(what = str_c(what, ", ", where, "<br>", additional_info)) %>% 
  select(year_begin, what) %>% 
  arrange(desc(year_begin)) %>% 
  kable(align = c('l', 'l'))
```

<!-- <br class="pageBreak"> -->

## Personal skills & volunteering {.personal .nohead .set-width}
```{r}
cv_entries %>%
  filter(type == 'volunteering' & professional_2_page == 'y') %>%
  mutate(what = str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where)) %>%
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%
  arrange(order, desc(year_end), desc(year)) %>%
  select(year, what) %>%
  kable()
```

<!-- <br class="pageBreak"> -->

### Links
