---
title: "Ulrik Lyngs <br> Curriculum vitae"
#date: "`r Sys.Date()`"
output:
  pagedown::html_paged:
    # change to true for a self-contained document, but it'll be a litte slower for Pandoc to render
    self_contained: false
    css: [ul_style.css, "https://stackpath.bootstrapcdn.com/bootstrap/4.3.1/css/bootstrap-grid.min.css"]
    #template: ul_template.html
    template: paged.html
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)


#### create publications table #####
publications <- readxl::read_xlsx("../cv_data/publications.xlsx")

pub_table <- publications %>%
  mutate(other = replace_na(other, "")) %>% 
  mutate(author_year = str_c("*", authors, " (", year, ")*. ")) %>%  #italicise authors and year
  mutate(title = str_c("[", title, "](", url, ")")) %>% #turn title into link
  mutate(citation = str_c(author_year, title, venue, other, sep = " ")) %>%
  select(citation) %>% 
  mutate(citation = str_replace(citation, "Lyngs, U.", "__Lyngs, U.__")) %>% # make my name bold
  knitr::kable()


#### create education table #####
cv_entries <- readxl::read_xlsx("../cv_data/cv_entries.xlsx")

edu_table <- cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year, what) %>% 
  kable()

#### create grants and awards table #####
awards_table <- cv_entries %>% 
  filter(type == 'grants_and_awards') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year, what) %>% 
  kable()

#### create service table #####
service_table <- cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(where = ifelse(!is.na(url), str_c("[", where, "](", url, ")"), where)) %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year, what) %>% 
  kable()


#### create talks table #####
talk_table <- cv_entries %>% 
  filter(type == 'talk') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year, what) %>% 
  kable()


#### create poster table ####
poster_table <- cv_entries %>% 
  filter(type == 'poster') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year, what) %>% 
  kable()


```


```{r, include=FALSE}
#### create prof dev table ####
prof_dev <- cv_entries %>% 
  filter(type == 'prof-dev') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year, what) %>% 
  kable()


#### create media table ####
media <- cv_entries %>% 
  filter(type == 'media') %>% 
  select(year, what) %>% 
  kable()
```


```{r, include=FALSE}
#### create work experience table ####
work <- cv_entries %>% 
  filter(type == 'work') %>% 
  mutate(what = str_c(what, ", ", where, ", ", additional_info)) %>% 
  select(year, what) %>% 
  kable()

#### create work experience table ####
technical <- cv_entries %>% 
  filter(type == 'technical') %>% 
  mutate(what = str_c(what, ", ", additional_info)) %>% 
  select(what) %>% 
  kable()

```





<div class="row">

```{block type="col-6"}
# Personal summary {.summary}
I am a cognitive psychologist-turned-computer scientist. I am passionate about applying insights from the behavioural neurosciences to design digital technology that is sensitive to human limitations and biases, particularly in relation to attention and self-regulation.

```

```{block type='col-6'}
# info box {.box}
<div class="info-box">
Department of Computer Science,\
University of Oxford, Oxford, UK

+44 (0)7472 185588\
ulrik.lyngs\@cs.ox.ac.uk\
ulriklyngs.com
</div>

```

</div>


<div class="row">

<div class='col-6 left'>
# Selected Publications {.publications}

`r pub_table`

</div>



<div class='col-6 right'>
# Education {.education}

`r edu_table`

# Grants and Awards {.grants}

`r awards_table`

# Service {.service}

`r service_table`

</div>


<!-- here ends the row i.e. the first page -->
</div>

<br class="pageBreak" />

<!-- here starts the news row i.e. the second page -->
<div class="row">

<div class="col-6 left">
# Selected talks {.talks}

`r talk_table`

# Selected poster presentations {.posters}

`r poster_table`

</div


<div class="col-6 right">
# Professional development {.prof-dev}

`r prof_dev`

# Media coverage {.media}

`r media`

# Selected work experience {.work}

`r work`

# Technical skills {.technical}

`r technical`

</div>


<!-- here ends the second page -->
</div>
