---
title: "Ulrik Lyngs: CV"
output:
  html_document:
    css: ["css/make-cv-like-other.css", "css/one-column-cv.css", "css/website-page.css", "css/style.css", "https://use.fontawesome.com/releases/v5.7.2/css/all.css"]
    toc: true
    toc_float: true

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(knitr)
library(here)
library(DT)
library(lubridate)

#### publications #####
publications <- read_csv("_content/publications.csv")

#### cv entries #####
cv_entries <- read_csv("_content/cv_entries.csv") %>% 
  mutate(year_begin = year(date)) %>%
  mutate(year_end = case_when(
    date_end == "present" ~ date_end,
    !is.na(date_end) ~ str_sub(date_end, 1, 4),
    is.na(date_end) ~ date_end
  )) %>%
  mutate(year = ifelse((is.na(year_end) | year_begin == year_end),
                      year_begin,
                      str_c(year_begin, " --- ", year_end)))

```

<br>

# Summary

I am passionate about using insights from the behavioural neurosciences to **design digital technology that is sensitive to human limitations and biases**, particularly in relation to attention and self-regulation.

My **academic and professional background** is highly interdisciplinary, and I try to integrate best practices from many work spheres, such as using tools from large-scale event management to structure academic projects.

My **personal interests** include travelling & couchsurfing, samatha meditation, dancing (Cuban salsa and swing), and playing music (whatever instruments I can get my hands on, and ideally with the [Karaoke Collective](https://karaokecollective.com)).

Download a brief version of [my CV as PDF](https://github.com/ulyngs/pagedown-cv/raw/master/_pdfs/lyngs_cv_2019_june.pdf).

<br>

# Academia
## Education {.education .nohead}
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year, what) %>% 
  kable()
```

## Research {.tabset .output-header}
### Publications {.nohead .publications}
```{r}
publications_table <- publications %>%
  arrange(desc(date), type) %>%
  mutate(author_year = str_c(authors_full, " (", year(date), "). ")) %>%
  mutate(title = ifelse(!is.na(url), str_c("[", title, "](", url, ")"), title)) %>% #turn title into link
  mutate(citation = ifelse(!is.na(award),
                           str_c(author_year, title, venue, "<i class='fas fa-award'></i><em>", award, "</em>", sep = " "),
                           str_c(author_year, title, venue, sep = " "))) %>%
  mutate(citation = str_replace(citation, "Ulrik Lyngs", "_Ulrik Lyngs_")) %>%  # make my name italicised
  filter(type != "master's thesis") %>%
  select(type, citation)


publications_table %>%
  knitr::kable()

```

### Talks {}
```{r}
cv_entries %>% 
  filter(type == 'talk') %>% 
  mutate(where = str_replace(where, "\\[([^]]*)\\]\\(([^\\s^\\)]*)[\\s\\)]", "<a href='\\2'>\\1</a>")) %>% 
  mutate(what = str_c("<em>", what, "</em>, ", where)) %>% 
  select(Date = date, Talk = what) %>% 
  mutate(Date = as_date(Date)) %>% 
  arrange(desc(Date)) %>% 
  mutate(Date = str_c(year(Date),
                      ", ",
                      month(Date, label = TRUE))) %>% 
  datatable(rownames = FALSE, escape = FALSE, class = 'row-border', options = list(
  pageLength = 10
))

  
```

### Posters {.nohead .posters}
```{r}
cv_entries %>% 
  filter(type == 'poster') %>%
  mutate(what = str_c("*", what, "*, ", where)) %>% 
  select(year_begin, what) %>% 
  arrange(desc(year_begin)) %>% 
  kable()
```

## Teaching experience {.teaching .service .nohead}
```{r}
cv_entries %>% 
  filter(type == 'teaching') %>% 
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info),
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where))) %>% 
  select(year, what) %>% 
  kable()
```

## Other {.tabset .output-header}
### Grants and Awards {.grants .nohead}
```{r}
cv_entries %>% 
  filter(type == 'grants_and_awards') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year_begin, what) %>% 
  kable()

```


### Media coverage {.media .nohead}
```{r}
cv_entries %>% 
  filter(type == 'media') %>%
  select(year_begin, what) %>% 
  kable()
```

### Service {.service .nohead}
```{r}
cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(year_end = ifelse(year_end == "present", "", year_end)) %>%
  mutate(where = ifelse(!is.na(url), str_c("[", where, "](", url, ")"), where)) %>% 
  mutate(what = ifelse(!is.na(additional_info),
                       str_c(what, "<br class='work-break'>", where),
                      str_c(what, "<br class='work-break'>", where))) %>% 
  select(year, what) %>% 
  kable()

```


# Work (non-academia)
## Selected work experience {.work .nohead .vertical-top}
```{r}
cv_entries %>% 
  filter(type == 'work', is.na(website)) %>% 
  mutate(additional_info = replace_na(additional_info, "")) %>% 
  mutate(what = str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info)) %>% 
  arrange(desc(year_begin)) %>% 
  select(year, what) %>% 
  kable()
```

## Professional development {.prof-dev .nohead}
```{r}
cv_entries %>% 
  filter(type == 'prof-dev') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year_begin, what) %>% 
  kable()
```

# Technical
## Software development {.cv-table .nohead .vertical-top}
```{r}
cv_entries %>% 
  filter(type == 'programming') %>% 
  replace_na(list(where = "", additional_info = "")) %>% 
  mutate(what = str_c(what, ", ", where, "<br>", additional_info)) %>% 
  select(year_begin, what) %>% 
  arrange(desc(year_begin)) %>% 
  kable(align = c('l', 'l'))
```

## Skills {.technical .nohead}
```{r}
cv_entries %>% 
  filter(type == 'technical') %>% 
  mutate(what = str_c("- *", what, "* ", additional_info)) %>% 
  select(what) %>% 
  kable()
```


# Personal
## Skills & volunteering {.personal .service .nohead}
```{r}
cv_entries %>%
  filter(type == 'volunteering') %>%
  mutate(what = str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where)) %>%
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%
  arrange(desc(year), desc(year_end)) %>%
  select(year, what) %>%
  kable()
```


